\chapter{Introduction}
%TODO Co czytuajacy potrzebuje wiedziec zeby zrozumiec prace? 
%TODO co to jest deep learning, analiza szeregow czasowych, tetno, cisnienie krwi, czemu pacjenci moga zemdlec

%TODO Jaki konkretnie aspekt tematu bedzie poruszony?
%TODO Skupiam sie na analizie tetna i cisnienia krwi pacjentow za pomoca deep learningu w sposob nienadzorowany

%TODO Czy podobne rzeczy zostaly juz opracowane?
%TODO nie, robiono takie rzeczy w inny sposob, albo dla innych danych

\quad Nowadays, deep learning is applied in many areas of life. A lot of companies compete to create the best artificial intelligence model specialized in specific tasks. Fields of study where deep learning is developing the fastest are image and text/speech processing. In this way, problems such as image recognition, image captioning, text translation or understanding speech are the matter of utilizing appropriate model prepared by specialists. It's very convenient, because crafting such a model is very demanding task and require a lot of data and computational power, which is usually not available to average people.

Health is important to everyone. Many technological advances help save people's health and lives. It is no different with deep learning. Detecting malicious tumors on X-rays is successfully used for many years. Basic life functions are simply series of data in time that can be freely monitored by artificial intelligence models. This allows to effectively detect health and life hazards in real time.   



\section{Goals}
%TODO Co badania maja rozkminic i jak?
%TODO badania maja znalec najlepszy model do wykrywania anomalii w szeregach czasowych ktory pozwoli na badanie pacjentow w czasie rzeczywistym

\quad The goal of this dissertation is to research available deep learning algorithms allowing classification of time series in the form of heart rate and blood pressure. As an additional aim the best model should be adapted to the real time data processing to utilize it in practice to warn patients about fainting. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text. Temporary text.


\section{Scope}
%TODO Co kazdy rodzial wnosi do pracy?

\quad This document is divided into a few main parts, as following:
\begin{enumerate}
	\item \textbf{Introduction}
	\\Briefly discusses the topic, describes assumed goals and explains why this work is important.
	\item \textbf{State Of The Art}
	\\Presents papers discussing latest achievements in similar fields of study. 
	\item \textbf{Background}
	\\Describes the data, explains utilized deep learning algorithms in depth, outlines used frameworks and libraries.
	\item \textbf{Experiments}
	\\Presents experimental setup, testing methodology and the way experiments were carried out.
	\item \textbf{Results}
	\\Explains the results obtained from experiments extensively. 
	\item \textbf{Conclusions}
	\\Presents conclusions drawn from experiments' analyzes and proposes future work.
\end{enumerate}

%TODO podsumowanie?






